LDpred2: better, faster, stronger

### 2020-03-28 paper/paper-ldpred2.tex
start intro

\title{Efficient toolkit implementing best practices for principal component analysis of population genetic data}
\author{Florian Priv\'e,$^{\text{1,}*}$ and Bjarni J. Vilhj\'almsson$^{\text{1,}*}$}

@@

@@

@@

>>>>

\title{LDpred2: better, faster, stronger}
\author{Florian Priv\'e,$^{\text{1,}*}$ and Bjarni J. Vilhj\'almsson$^{\text{1,}*}$}

@@

\vspace*{4em}

@@

The use of polygenic scores (PGS) is widespread now.
There are high hopes for using these scores, which sum up the information of many genetic variants into a single score, into clinical practice. 
Predictive performance of PGS is inexorably bounded by heritability, the proportion of phenotypic variance that is attributable to genetics, so that their possibility of being used as a diagnostic tool for diseases is limited.
Nevertheless, it should be possible to use them to stratify the population into groups of different risk levels, to be able to identify individuals at high risk for a given disease [CITATION]. 
These people should then be monitored more closely to detect the disease and intervene sooner to maximize chances of remission (e.g.\ in the case of cancer).
PGS are also extensively used in epidemiology and economics as predictive variables of interest. For example, a recently derived PGS for education attainment has been the most predictive variable in social sciences so far [CITATION].

LDpred is a popular and powerful method for deriving polygenic scores based on summary statistics and a Linkage Disequilibrium (LD) matrix only \cite[]{vilhjalmsson2015modeling}.
It assumes there is a proportion $p$ of variants that are causal.
However, LDpred currently has several limitations that may result in limited predictive performance.
The non-infinitesimal version of LDpred, a Gibbs sampler, is particularly sensitive to model misspecification when applied to summary statistics with large sample sizes.
It may also be very unstable in long-range LD regions such as the human leukocyte antigen (HLA) region of chromosome 6. This issue has lead to the removal of this region from analyses  \cite[]{marquez2018modeling,lloyd2019improved}, which is a shame since this region of the genome contains several disease-associated variants, particularly with autoimmune diseases and psychiatric disorders [CITATIONS].
LDpred is also considered not particularly fast, nor memory-efficient, nor it provides truly sparse models as in its model specification.

Here, we present LDpred2, a new version of LDpred, that aims to cope with the issues presented before.
We show that [DESCRIBE RESULTS].

@@

\subsection{Overview of Methods}
